Commutative Character Sheaves

### 2015-10-10 followup.tex
Added proof that G --> Gab exists in Fq-schemes.

\subsection{Derived subgroup}

@@

\subsection{Abelianization}

Let $q: G \to G\ab$ be the fppf-quotient  . . . 
We suppose $G\ab$ exists in group schemes over $\Fq$. \todo{This is a condition on $G$. Does it follow from smoothness? I've written to Masoud for help on this.}
If $G$ is of finite type (and so, an algebraic group) then $G\ab$ exists in group schemes by \cite{GM}*{Thm 4.39}: $G$ smooth implies $G$ flat; $G\der$ is also smooth (!) so also flat; $\dim \Spec{\Fq} \leq 1$.

\[
\begin{tikzcd}
{} & G\times G \arrow{d}{} &&&\\
1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
\end{tikzcd}
\]

>>>>

\subsection{Derived subgroup and abelianization}

@@

The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ by SGA3, Expos\'e VI, Tome B, Th\'eor\`eme 3.2, which also shows that the quotient $G \to G\ab$ is a faithfully flat and a $G$-torsor in the fppf topology.
\[
\begin{tikzcd}
{} & G\times G \arrow{d}{} &&&\\
1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
\end{tikzcd}
\]
